Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}

```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}

```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}

```

***

### User Ages
Notes:

```{r User Ages}

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

```{r Quiz 1}

library(ggplot2)
data(diamonds)

diam <- diamonds
str(diam)
by(diam, diam$color, nrow)
```

***

```{r Quiz 2}

ggplot(diam, aes(x = price)) + geom_histogram()

```

***

```{r Quiz 3}

summary(diam$price)

```
***

```{r Quiz 4}

library(dplyr)
nrow(filter(diam, price < 500))
nrow(filter(diam, price < 250))
nrow(filter(diam, price >= 15000))

```
***

```{r Quiz 5}

ggplot(diam, aes(x = price), binwidth(10)) + geom_histogram() + xlim(0,2000)


```
***

```{r Quiz 6}

ggplot(diam, aes(x = price), binwidth(10)) + geom_histogram() + facet_wrap(~diam$cut)


```
***

```{r Quiz 7}

by(diam$price, diam$cut, max)
by(diam$price, diam$cut, min)
by(diam$price, diam$cut, median)


```
***

```{r Quiz 8}

ggplot(diam, aes(x = price), binwidth(10)) + geom_histogram() + facet_wrap(~cut, scales = "free")



```

***

```{r Quiz 9}

ggplot(diam, aes(x = log10(price/carat)), binwidth(10)) + geom_histogram() + facet_wrap(~cut, scales = "free")



```

***
```{r Quiz 10}

ggplot(diam, aes(x = price, y = carat), binwidth(10)) + geom_boxplot() + facet_wrap(~clarity, scales = "free")
ggplot(diam, aes(x = price, y = carat), binwidth(10)) + geom_boxplot() + facet_wrap(~cut, scales = "free")
ggplot(diam, aes(x = price, y = carat), binwidth(10)) + geom_boxplot() + facet_wrap(~color, scales = "free")



```
***
```{r Quiz 11}
library(stats)

by(diam, diam$color, summary)
IQR(filter(diam, color == "D")$price)
IQR(filter(diam, color == "J")$price)

```
***
```{r Quiz 12}
library(stats)

ggplot(diam, aes(x = length(1:nrow(diam)),y = price/carat), binwidth(10)) + geom_boxplot() + facet_wrap(~color, scales = "free")

```
***
```{r Quiz 13}
library(stats)

ggplot(diam, aes(x = carat)) + geom_freqpoly() + stat_bin(binwidth = 0.01) +  ylim(0,3000)
nrow(filter(diam, carat == 3))


```
***
```{r Quiz 14}
library(lubridate)

ggplot(diam, aes(x = carat)) + geom_freqpoly() + stat_bin(binwidth = 0.01) +  ylim(0,3000)
nrow(filter(diam, carat == 3))


```
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!