Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

```{r Overplotting}

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

library(ggplot2)
library(readr)
pf <- read_tsv("pseudo_facebook.tsv")
ggplot(pf, aes(x = age, y = friend_count)) + geom_point(alpha = 1/20) + coord_trans(y = "sqrt")


```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}


ggplot(pf, aes(x = age, y = friendships_initiated)) + geom_point(alpha = 1/10, position = "jitter")


```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

library(dplyr)
library(ggplot2)

groups <- group_by(pf, age)
pf.fc_by_age <- summarize(groups, mean_fc = mean(friend_count))
ggplot(pf.fc_by_age, aes(x = age, y = mean_fc)) + geom_line()

```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

with(pf, cor.test(pf$age, pf$friend_count))

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, pf$age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

ggplot(pf, aes(x = www_likes_received, y = likes_received)) + geom_point()

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}



```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

cor.test(pf$www_likes_received, pf$likes_received, method = "pearson")

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
attach(Mitchell)
data("Mitchell")

ggplot(Mitchell, aes(x = Month, y = Temp)) + geom_point() + scale_x_discrete(breaks = seq(0, 203, 12))
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

0

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

cor.test(Mitchell$Month, Mitchell$Temp)

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

pf$age_with_months <- pf$age+(1-pf$dob_month/12)

```

***

### Age with Months Means

```{r Age with Months Means}



```

Programming Assignment
```{r Programming Assignment}

groups <- group_by(pf, age_with_months)
pf.fc_by_age_months <- summarize(groups, 
                                 friend_count_mean = mean(friend_count),
                                 friend_count_median = median(friend_count),
                                 n = n())


```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

ggplot(subset(pf.fc_by_age_months, age < 71), aes(x = age, y = friend_count_mean)) + geom_line()

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

