Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_histogram()
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
getwd()
setwd("/Users/Kharitonov/Desktop/udacity_r/lesson4")
pf <- read_tsv("/Users/Kharitonov/Desktop/udacity_r/lesson4/pseudo_facebook.tsv")
pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>% 
  group_by(age, gender) %>% 
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>% 
  ungroup() %>% 
  arrange(age)

ggplot(pf.fc_by_age_gender, aes(x = age, y = median_friend_count, color = gender)) + 
  geom_line()
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
library(tidyr)

spread(subset(pf.fc_by_age_gender, select = c('gender', 'age', 'median_friend_count')), gender, median_friend_count)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender, value.var = "median_friend_count")

```


***

### Ratio Plot
Notes:

```{r Ratio Plot}

ggplot(pf.fc_by_age_gender.wide, aes(y = female/male, x = age)) + geom_line() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

pf$year_joined <- 2014 - ceiling(pf$tenure/365)

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}

pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(subset(pf, !is.na(year_joined.bucket)), aes(x = age, y = friend_count)) + 
  geom_line(aes(color = year_joined.bucket),fun.y = mean, stat = "summary")

```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(subset(pf, !is.na(year_joined.bucket)), aes(x = age, y = friend_count)) + 
  geom_line(aes(color = year_joined.bucket),fun.y = mean, stat = "summary") +
  geom_line(fun.y = mean, linetype = "dashed", stat = "summary")
```

***

### Friending Rate
Notes:

```{r Friending Rate}
library(dplyr)

pf_friends <- pf %>% filter(tenure > 0) %>%  mutate(friending_rate = friend_count/tenure)

max(pf_friends$friending_rate)

```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}

pf_friends <- pf_friends %>% mutate(friendshipping_rate = friendships_initiated/tenure)

ggplot(pf_friends, aes(x = tenure, y = friendshipping_rate)) +
  geom_smooth(aes(color = year_joined.bucket), fun.y = mean)

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

yo <- read.csv("yogurt.csv")
yo$id <- factor(yo$id)

ggplot(yo, aes(x = price)) + geom_histogram(binwidth = 10)

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

yo <- yo %>% mutate(all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)

```

***

### Prices over Time
Notes:

```{r Prices over Time}

ggplot(yo, aes(x = time, y = price)) + geom_point(alpha = 0.05)

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

set.seed(1313)
sample_id <- sample(levels(yo$id),18, replace = FALSE)

ggplot(subset(yo, id %in% sample_id), aes(x = time, y = price)) +
  facet_wrap(~id) +
  geom_line() +
  geom_point(size = yo$all.purchases)


```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

```{r Scatterplot Matrix}

install.packages("GGally")
library(GGally)

set.seed(1836)
ggpairs(pf_subset[sample.int(nrow(pf), 1000), -1] )
pf_subset <- pf[sample.int(nrow(pf), 1000),]

cor.test(pf_subset$friendships_initiated, pf_subset$friend_count)
cor.test(pf_subset$age, pf_subset$mobile_likes)


```

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

